BIP-Predictor

### 2025-05-22 Sweave/BIP_predictor.Rnw
up

# Settings for M-SSA
ht_mssa_vec<-c(6.380160,  6.738270,   7.232453,   7.225927,   7.033768)
f_excess<-c(5,rep(4,length(select_vec_multi)-1))
# In-smaple span for VAR
date_to_fit<-"2008"
# Model orders
p<-1
q<-0
# Filter length
L<-31
# Publication lag: one quarter for BIP
lag_vec<-c(1,rep(0,ncol(x_mat)-1))

# Use OLS or WLS in regression of shifted BIP on M-SSA component predictor 
use_garch<-F

@@

# Without Covid
# Full sample

if (recompute_results)
{
  data_fit<-x_mat

  set.seed(12)
  V_obj<-VARMA(data_fit,p=p,q=q)
  threshold<-1.5
  V_obj<-refVARMA(V_obj, thres = threshold)
  save(V_obj,file=paste(path.result,"/VAR",sep=""))
# Without Pandemic  
  data_fit<-x_mat_wc
  set.seed(12)
  V_obj_wc<-VARMA(data_fit,p=p,q=q)
  threshold<-1.5
  V_obj_wc<-refVARMA(V_obj_wc, thres = threshold)
  save(V_obj_wc,file=paste(path.result,"/VAR_wc",sep=""))

} else
{
    load(file=paste(path.result,"/VAR",sep=""))
    load(file=paste(path.result,"/VAR_wc",sep=""))

@@

# We rely on data with Pandemic
#   -M-SSA is not affected since the in-sample span ends in 2008
if (recompute_results)
{
# Run the wrapper, see tutorial 7.2
#   -The function computes M-SSA for each forecast horizon h in h_vec
  mssa_indicator_obj<-compute_mssa_BIP_predictors_func(x_mat,lambda_HP,L,date_to_fit,p,q,ht_mssa_vec,h_vec,f_excess,lag_vec,select_vec_multi)

@@

  mssa_indicator_HP_HT_obj<-compute_mssa_BIP_predictors_func(x_mat,lambda_HP,L,date_to_fit,p,q,ht_mssa_vec_HP_C,h_vec,f_excess,lag_vec,select_vec_multi)

  save(mssa_indicator_obj,file=paste(path.result,"/nowcast_obj",sep=""))
  save(mssa_indicator_HP_HT_obj,file=paste(path.result,"/nowcast_HT_HP_obj",sep=""))
} else
{
  load(file=paste(path.result,"/nowcast_obj",sep=""))
  load(file=paste(path.result,"/nowcast_HT_HP_obj",sep=""))
}

@@

if (recompute_results)
{
# Run the wrapper, see tutorial 7.2
#   -The function computes M-SSA for each forecast horizon h in h_vec
  mssa_indicator_obj<-compute_mssa_BIP_predictors_func(x_mat,lambda_HP,L,date_to_fit,p,q,ht_mssa_vec,h_vec,f_excess,lag_vec,select_vec_multi)
# Without pandemic  
  mssa_indicator_obj_wc<-compute_mssa_BIP_predictors_func(x_mat_wc,lambda_HP,L,date_to_fit,p,q,ht_mssa_vec,h_vec,f_excess,lag_vec,select_vec_multi)

  save(mssa_indicator_obj,file=paste(path.result,"/mssa_indicator_obj",sep=""))
  save(mssa_indicator_obj_wc,file=paste(path.result,"/mssa_indicator_obj_wc",sep=""))
} else
{
  load(file=paste(path.result,"/mssa_indicator_obj",sep=""))
  load(file=paste(path.result,"/mssa_indicator_obj_wc",sep=""))
}
# Target series: output of two-sided HP applied to BIP: 
#   -This is the target for which the original M-SSA predictor (tutorial 7.3) has been designed
#   -The target is forward-shifted by the forecast horizon (plus publication lag)
target_shifted_mat<-mssa_indicator_obj$target_shifted_mat
# Original M-SSA predictor, see tutorial 7.3
#   -One predictor available for each forecast horizon in h_vec
predictor_mssa_mat<-mssa_indicator_obj$predictor_mssa_mat
# M-SSA components, see tutorial 7.2
#   -This is a three dimensional array
#   -For each forecast horizon and for each indicator we obtain the M-SSA predictor when targeting 
#     the two-sided HP applied to this indicator, see exercise 1.1 below
mssa_array<-mssa_indicator_obj$mssa_array
# Same but M-MSE
mmse_array<-mssa_indicator_obj$mmse_array

@@

# Assign column and rownames
  colnames(p_mat_mssa_components)<-colnames(p_mat_direct)<-colnames(p_mat_mssa_components_without_covid)<-
    colnames(rRMSE_mSSA_comp_direct)<-colnames(rRMSE_mSSA_comp_mean)<-
    colnames(rRMSE_mSSA_comp_direct_without_covid)<-colnames(rRMSE_mSSA_comp_mean_without_covid)<-
    colnames(rRMSE_mSSA_direct_mean)<-colnames(rRMSE_mSSA_direct_mean_without_covid)<-
    colnames(p_mat_direct_without_covid)<-colnames(MSE_oos_mssa_comp_mat)<-
    colnames(MSE_oos_mssa_comp_without_covid_mat)<-paste("h=",h_vec,sep="")
  rownames(p_mat_mssa_components)<-rownames(p_mat_direct)<-rownames(p_mat_mssa_components_without_covid)<-
    rownames(rRMSE_mSSA_comp_direct)<-rownames(rRMSE_mSSA_comp_mean)<-
    rownames(rRMSE_mSSA_comp_direct_without_covid)<-rownames(rRMSE_mSSA_comp_mean_without_covid)<-
    rownames(rRMSE_mSSA_direct_mean)<-rownames(rRMSE_mSSA_direct_mean_without_covid)<-
    rownames(p_mat_direct_without_covid)<-rownames(MSE_oos_mssa_comp_mat)<-
    rownames(MSE_oos_mssa_comp_without_covid_mat)<-paste("Shift=",shift_vec,sep="")
# Define list for saving all matrices  
    list_perf<-list(p_mat_mssa_components=p_mat_mssa_components,p_mat_direct=p_mat_direct,
    p_mat_mssa_components_without_covid=p_mat_mssa_components_without_covid,rRMSE_mSSA_comp_direct=rRMSE_mSSA_comp_direct,
    rRMSE_mSSA_comp_mean=rRMSE_mSSA_comp_mean, rRMSE_mSSA_comp_direct_without_covid=rRMSE_mSSA_comp_direct_without_covid,
    rRMSE_mSSA_comp_mean_without_covid=rRMSE_mSSA_comp_mean_without_covid,rRMSE_mSSA_direct_mean=rRMSE_mSSA_direct_mean,
    rRMSE_mSSA_direct_mean_without_covid=rRMSE_mSSA_direct_mean_without_covid,p_mat_direct_without_covid=p_mat_direct_without_covid,
    final_components_preditor_array=final_components_preditor_array,oos_components_preditor_array=oos_components_preditor_array,track_weights_array=track_weights_array,MSE_oos_mssa_comp_mat=MSE_oos_mssa_comp_mat,
    MSE_oos_mssa_comp_without_covid_mat=MSE_oos_mssa_comp_without_covid_mat)
# The results can be saved (overwritten)    
    if (F)
    {
      save(list_perf,file=paste(path.result,"list_perf",sep=""))
    }
} else
{
# Load all results  
  load(file=paste(path.result,"list_perf",sep=""))
  p_mat_mssa_components=list_perf$p_mat_mssa_components
  p_mat_direct=list_perf$p_mat_direct
  p_mat_mssa_components_without_covid=list_perf$p_mat_mssa_components_without_covid
  rRMSE_mSSA_comp_direct=list_perf$rRMSE_mSSA_comp_direct
  rRMSE_mSSA_comp_mean=list_perf$rRMSE_mSSA_comp_mean
  rRMSE_mSSA_comp_direct_without_covid=list_perf$rRMSE_mSSA_comp_direct_without_covid
  rRMSE_mSSA_comp_mean_without_covid=list_perf$rRMSE_mSSA_comp_mean_without_covid
  rRMSE_mSSA_direct_mean=list_perf$rRMSE_mSSA_direct_mean
  rRMSE_mSSA_direct_mean_without_covid=list_perf$rRMSE_mSSA_direct_mean_without_covid
  p_mat_direct_without_covid=list_perf$p_mat_direct_without_covid  
  final_components_preditor_array=list_perf$final_components_preditor_array
  oos_components_preditor_array=list_perf$oos_components_preditor_array
  track_weights_array=list_perf$track_weights_array
  MSE_oos_mssa_comp_mat=list_perf$MSE_oos_mssa_comp_mat
  MSE_oos_mssa_comp_without_covid_mat=list_perf$MSE_oos_mssa_comp_without_covid_mat
}

@@

# We can select type of VAR model
VAR_type="BVAR"
VAR_type="VAR"
if (VAR_type=="BVAR")
{
# Simon's settings for BVAR(4)  
  lambda_BVAR <- 10 
  p_full<-4
  q_full<-0
}
if (VAR_type=="VAR")
{
# Marc's settings for VAR  
  p_full<-p
  q_full<-q
}

# Run the M-SSA wrapper, see tutorial 7.2
#   -The function computes M-SSA and M-MSE for each forecast horizon h in h_vec
if (recompute_results)
{
  final_mssa_indicator_obj<-compute_mssa_BIP_predictors_func(x_mat_wc,lambda_HP,L,date_to_fit_all,p_full,q_full,ht_mssa_vec,h_vec,f_excess,lag_vec,select_vec_multi,VAR_type,lambda_BVAR)
  save(final_mssa_indicator_obj,file=paste(path.result,"/final_mssa_indicator_obj",sep=""))
} else
{
  load(file=paste(path.result,"/final_mssa_indicator_obj",sep=""))
}
# Final M-SSA components
final_mssa_array<-final_mssa_indicator_obj$mssa_array

@@

  set.seed(12)
  V_obj_full<-VARMA(data_fit,p=p,q=q)
  threshold<-1.5
  V_obj_full<-refVARMA(V_obj_full, thres = threshold)
  save(V_obj_full,file=paste(path.result,"/VAR_full",sep=""))

# VAR based on data pre 2008  
  data_fit<-x_mat_wc[which(rownames(x_mat_wc)<date_to_fit),]

  set.seed(12)
  V_obj_2008<-VARMA(data_fit,p=p,q=q)
  threshold<-1.5
  V_obj_2008<-refVARMA(V_obj_2008, thres = threshold)
  save(V_obj_2008,file=paste(path.result,"/VAR_2008",sep=""))

} else
{
    load(file=paste(path.result,"/VAR_full",sep=""))
    load(file=paste(path.result,"/VAR_2008",sep=""))

>>>>

# Settings for M-SSA
ht_mssa_vec<-c(6.380160,  6.738270,   7.232453,   7.225927,   7.033768)
f_excess<-c(5,rep(4,length(select_vec_multi)-1))
# In-smaple span for VAR
date_to_fit<-"2008"
# We can select type of VAR model
VAR_type="BVAR"
VAR_type="VAR"
if (VAR_type=="BVAR")
{
# Simon's settings for BVAR(4)  
  lambda_BVAR <- 0.001
  p<-3
  q<-0
}
if (VAR_type=="VAR")
{
# Marc's settings for VAR  
  p<-1
  q<-0
}

# Filter length
L<-31
# Publication lag: one quarter for BIP
lag_vec<-c(1,rep(0,ncol(x_mat)-1))

# Use OLS or WLS in regression of shifted BIP on M-SSA component predictor
# Default (better): use_garch<-F
use_garch<-F

@@

# Full sample estimation with/without pandemic
if (recompute_results)
{
# With pandemic  
  data_fit<-x_mat
  if (VAR_type=="VAR")
  {

    set.seed(12)
    V_obj<-VARMA(data_fit,p=p,q=q)
# Apply regularization: see vignette MTS package
    threshold<-1.5
    V_obj<-refVARMA(V_obj, thres = threshold)
    save(V_obj,file=paste(path.result,"/VAR",sep=""))
  }
  if (VAR_type=="BVAR")
  {
    V0_BVAR <- diag(rep(1,n))  # prior for Sigma_a matrix - K x K
    # precision matrix of size (kp+1) x (kp+1)  if there's a constant
    #   low values <=> low precision

    C_BVAR <- lambda_BVAR*diag(rep(1,n*p+1))
    V_obj <- BVAR(data_fit,p = p,C = C_BVAR,V0 = V0_BVAR)
    save(V_obj,file=paste(path.result,"/BVAR",sep=""))
  }
# Without Pandemic  
  data_fit<-x_mat_wc
  if (VAR_type=="VAR")
  {

    set.seed(12)
    V_obj<-VARMA(data_fit,p=p,q=q)
# Apply regularization: see vignette MTS package
    threshold<-1.5
    V_obj<-refVARMA(V_obj, thres = threshold)
    save(V_obj_wc,file=paste(path.result,"/VAR_wc",sep=""))  
  }
  if (VAR_type=="BVAR")
  {
    V0_BVAR <- diag(rep(1,n))  # prior for Sigma_a matrix - K x K
    # precision matrix of size (kp+1) x (kp+1)  if there's a constant
    #   low values <=> low precision
    C_BVAR <- lambda_BVAR*diag(rep(1,n*p+1))
    V_obj_wc <- BVAR(data_fit,p = p,C = C_BVAR,V0 = V0_BVAR)
    save(V_obj_wc,file=paste(path.result,"/BVAR_wc",sep=""))
  }

} else
{
  if (VAR_type=="VAR")
  {
    load(file=paste(path.result,"/VAR",sep=""))
    load(file=paste(path.result,"/VAR_wc",sep=""))
  } else
  {
    load(file=paste(path.result,"/BVAR",sep=""))
    load(file=paste(path.result,"/BVAR_wc",sep=""))
  }
}

@@

# We rely on data with Pandemic
#   -M-SSA is not affected since the in-sample span ends in 2008
if (recompute_results)
{
# Run the wrapper, see tutorial 7.2
#   -The function computes M-SSA for each forecast horizon h in h_vec
  mssa_indicator_obj<-compute_mssa_BIP_predictors_func(x_mat,lambda_HP,L,date_to_fit,p,q,ht_mssa_vec,h_vec,f_excess,lag_vec,select_vec_multi,VAR_type,lambda_BVAR)

@@

  mssa_indicator_HP_HT_obj<-compute_mssa_BIP_predictors_func(x_mat,lambda_HP,L,date_to_fit,p,q,ht_mssa_vec_HP_C,h_vec,f_excess,lag_vec,select_vec_multi,VAR_type,lambda_BVAR)
  if (VAR_type=="VAR")
  {
    save(mssa_indicator_obj,file=paste(path.result,"/nowcast_obj",sep=""))
    save(mssa_indicator_HP_HT_obj,file=paste(path.result,"/nowcast_HT_HP_obj",sep=""))
  }
  if (VAR_type=="BVAR")
  {
    save(mssa_indicator_obj,file=paste(path.result,"/BV_nowcast_obj",sep=""))
    save(mssa_indicator_HP_HT_obj,file=paste(path.result,"/BV_nowcast_HT_HP_obj",sep=""))
  }
} else
{
  if (VAR_type=="VAR")
  {
    load(file=paste(path.result,"/nowcast_obj",sep=""))
    load(file=paste(path.result,"/nowcast_HT_HP_obj",sep=""))
  }
  if (VAR_type=="BVAR")
  {
    load(file=paste(path.result,"/BV_nowcast_obj",sep=""))
    load(file=paste(path.result,"/BV_nowcast_HT_HP_obj",sep=""))
  }

@@

if (recompute_results)
{
# Run the wrapper, see tutorial 7.2
#   -The function computes M-SSA for each forecast horizon h in h_vec
  mssa_indicator_obj<-compute_mssa_BIP_predictors_func(x_mat,lambda_HP,L,date_to_fit,p,q,ht_mssa_vec,h_vec,f_excess,lag_vec,select_vec_multi,VAR_type,lambda_BVAR)
# Without pandemic  
  mssa_indicator_obj_wc<-compute_mssa_BIP_predictors_func(x_mat_wc,lambda_HP,L,date_to_fit,p,q,ht_mssa_vec,h_vec,f_excess,lag_vec,select_vec_multi,VAR_type,lambda_BVAR)
  if (VAR_type=="VAR")
  {
    save(mssa_indicator_obj,file=paste(path.result,"/mssa_indicator_obj",sep=""))
    save(mssa_indicator_obj_wc,file=paste(path.result,"/mssa_indicator_obj_wc",sep=""))
  }
  if (VAR_type=="BVAR")
  {
    save(mssa_indicator_obj,file=paste(path.result,"/BV_mssa_indicator_obj",sep=""))
    save(mssa_indicator_obj_wc,file=paste(path.result,"/BV_mssa_indicator_obj_wc",sep=""))
  }

} else
{
  if (VAR_type=="VAR")
  {
    load(file=paste(path.result,"/mssa_indicator_obj",sep=""))
    load(file=paste(path.result,"/mssa_indicator_obj_wc",sep=""))
  }
  if (VAR_type=="BVAR")
  {
    load(file=paste(path.result,"/BV_mssa_indicator_obj",sep=""))
    load(file=paste(path.result,"/BV_mssa_indicator_obj_wc",sep=""))
  }
}
# Target series: output of two-sided HP applied to BIP: 
#   -This is the target for which the original M-SSA predictor (tutorial 7.3) has been designed
#   -The target is forward-shifted by the forecast horizon (plus publication lag)
target_shifted_mat<-mssa_indicator_obj$target_shifted_mat
# Original M-SSA predictor, see tutorial 7.3
#   -One predictor available for each forecast horizon in h_vec
predictor_mssa_mat<-mssa_indicator_obj$predictor_mssa_mat
# M-SSA components, see tutorial 7.2
#   -This is a three dimensional array
#   -For each forecast horizon and for each indicator we obtain the M-SSA predictor when targeting 
#     the two-sided HP applied to this indicator, see exercise 1.1 below
mssa_array<-mssa_indicator_obj$mssa_array
# Same but M-MSE
mmse_array<-mssa_indicator_obj$mmse_array

@@

# Assign column and rownames
  colnames(p_mat_mssa_components)<-colnames(p_mat_direct)<-colnames(p_mat_mssa_components_without_covid)<-
    colnames(rRMSE_mSSA_comp_direct)<-colnames(rRMSE_mSSA_comp_mean)<-
    colnames(rRMSE_mSSA_comp_direct_without_covid)<-colnames(rRMSE_mSSA_comp_mean_without_covid)<-
    colnames(rRMSE_mSSA_direct_mean)<-colnames(rRMSE_mSSA_direct_mean_without_covid)<-
    colnames(p_mat_direct_without_covid)<-colnames(MSE_oos_mssa_comp_mat)<-
    colnames(MSE_oos_mssa_comp_without_covid_mat)<-paste("h=",h_vec,sep="")
  rownames(p_mat_mssa_components)<-rownames(p_mat_direct)<-rownames(p_mat_mssa_components_without_covid)<-
    rownames(rRMSE_mSSA_comp_direct)<-rownames(rRMSE_mSSA_comp_mean)<-
    rownames(rRMSE_mSSA_comp_direct_without_covid)<-rownames(rRMSE_mSSA_comp_mean_without_covid)<-
    rownames(rRMSE_mSSA_direct_mean)<-rownames(rRMSE_mSSA_direct_mean_without_covid)<-
    rownames(p_mat_direct_without_covid)<-rownames(MSE_oos_mssa_comp_mat)<-
    rownames(MSE_oos_mssa_comp_without_covid_mat)<-paste("Shift=",shift_vec,sep="")
# Define list for saving all matrices  
    list_perf<-list(p_mat_mssa_components=p_mat_mssa_components,p_mat_direct=p_mat_direct,
    p_mat_mssa_components_without_covid=p_mat_mssa_components_without_covid,rRMSE_mSSA_comp_direct=rRMSE_mSSA_comp_direct,
    rRMSE_mSSA_comp_mean=rRMSE_mSSA_comp_mean, rRMSE_mSSA_comp_direct_without_covid=rRMSE_mSSA_comp_direct_without_covid,
    rRMSE_mSSA_comp_mean_without_covid=rRMSE_mSSA_comp_mean_without_covid,rRMSE_mSSA_direct_mean=rRMSE_mSSA_direct_mean,
    rRMSE_mSSA_direct_mean_without_covid=rRMSE_mSSA_direct_mean_without_covid,p_mat_direct_without_covid=p_mat_direct_without_covid,
    final_components_preditor_array=final_components_preditor_array,oos_components_preditor_array=oos_components_preditor_array,track_weights_array=track_weights_array,MSE_oos_mssa_comp_mat=MSE_oos_mssa_comp_mat,
    MSE_oos_mssa_comp_without_covid_mat=MSE_oos_mssa_comp_without_covid_mat)
# The results can be saved (overwritten)    
  if (VAR_type=="VAR")
  {
    save(list_perf,file=paste(path.result,"list_perf",sep=""))
  }
  if (VAR_type=="BVAR")
  {
    save(list_perf,file=paste(path.result,"BV_list_perf",sep=""))
  }
} else
{
# Load all results
  if (VAR_type=="VAR")
  {
    load(file=paste(path.result,"list_perf",sep=""))
  }
  if (VAR_type=="BVAR")
  {
    load(file=paste(path.result,"BV_list_perf",sep=""))
  }
  p_mat_mssa_components=list_perf$p_mat_mssa_components
  p_mat_direct=list_perf$p_mat_direct
  p_mat_mssa_components_without_covid=list_perf$p_mat_mssa_components_without_covid
  rRMSE_mSSA_comp_direct=list_perf$rRMSE_mSSA_comp_direct
  rRMSE_mSSA_comp_mean=list_perf$rRMSE_mSSA_comp_mean
  rRMSE_mSSA_comp_direct_without_covid=list_perf$rRMSE_mSSA_comp_direct_without_covid
  rRMSE_mSSA_comp_mean_without_covid=list_perf$rRMSE_mSSA_comp_mean_without_covid
  rRMSE_mSSA_direct_mean=list_perf$rRMSE_mSSA_direct_mean
  rRMSE_mSSA_direct_mean_without_covid=list_perf$rRMSE_mSSA_direct_mean_without_covid
  p_mat_direct_without_covid=list_perf$p_mat_direct_without_covid  
  final_components_preditor_array=list_perf$final_components_preditor_array
  oos_components_preditor_array=list_perf$oos_components_preditor_array
  track_weights_array=list_perf$track_weights_array
  MSE_oos_mssa_comp_mat=list_perf$MSE_oos_mssa_comp_mat
  MSE_oos_mssa_comp_without_covid_mat=list_perf$MSE_oos_mssa_comp_without_covid_mat
}

@@

# Model orders
p_full<-p
q_full<-q

# Run the M-SSA wrapper, see tutorial 7.2
#   -The function computes M-SSA and M-MSE for each forecast horizon h in h_vec
if (recompute_results)
{
  final_mssa_indicator_obj<-compute_mssa_BIP_predictors_func(x_mat_wc,lambda_HP,L,date_to_fit_all,p_full,q_full,ht_mssa_vec,h_vec,f_excess,lag_vec,select_vec_multi,VAR_type,lambda_BVAR)

  if (VAR_type=="VAR")
  {
    save(final_mssa_indicator_obj,file=paste(path.result,"/final_mssa_indicator_obj",sep=""))
  }
  if (VAR_type=="BVAR")
  {
    save(final_mssa_indicator_obj,file=paste(path.result,"/BV_final_mssa_indicator_obj",sep=""))
  }
} else
{
  if (VAR_type=="VAR")
  {
    load(file=paste(path.result,"/final_mssa_indicator_obj",sep=""))
  }
  if (VAR_type=="BVAR")
  {
    load(file=paste(path.result,"/BV_final_mssa_indicator_obj",sep=""))
  }
}
# Final M-SSA components
final_mssa_array<-final_mssa_indicator_obj$mssa_array

@@

  if (VAR_type=="VAR")
  {
    set.seed(12)
    V_obj_full<-VARMA(data_fit,p=p,q=q)
    threshold<-1.5
    V_obj_full<-refVARMA(V_obj_full, thres = threshold)
    save(V_obj_full,file=paste(path.result,"/VAR_full",sep=""))
  }
  if (VAR_type=="BVAR")
  {
    V0_BVAR <- diag(rep(1,n))  # prior for Sigma_a matrix - K x K
    # precision matrix of size (kp+1) x (kp+1)  if there's a constant
    #   low values <=> low precision
    C_BVAR <- lambda_BVAR*diag(rep(1,n*p+1))
    V_obj_full <- BVAR(data_fit,p = p,C = C_BVAR,V0 = V0_BVAR)
    save(V_obj_full,file=paste(path.result,"/BVAR_full",sep=""))
  }

# VAR based on data pre 2008  
  data_fit<-x_mat_wc[which(rownames(x_mat_wc)<date_to_fit),]
  if (VAR_type=="VAR")
  {
    set.seed(12)
    V_obj_2008<-VARMA(data_fit,p=p,q=q)
    threshold<-1.5
    V_obj_2008<-refVARMA(V_obj_2008, thres = threshold)
    save(V_obj_2008,file=paste(path.result,"/VAR_2008",sep=""))
  }
  if (VAR_type=="BVAR")
  {
    V0_BVAR <- diag(rep(1,n))  # prior for Sigma_a matrix - K x K
    # precision matrix of size (kp+1) x (kp+1)  if there's a constant
    #   low values <=> low precision
    C_BVAR <- lambda_BVAR*diag(rep(1,n*p+1))
    V_obj_2008 <- BVAR(data_fit,p = p,C = C_BVAR,V0 = V0_BVAR)
    save(V_obj_2008,file=paste(path.result,"/BVAR_2008",sep=""))
  }

} else
{
  if (VAR_type=="VAR")
  {
    load(file=paste(path.result,"/VAR_full",sep=""))
    load(file=paste(path.result,"/VAR_2008",sep=""))
  }
  if (VAR_type=="BVAR")
  {
    load(file=paste(path.result,"/BVAR_full",sep=""))
    load(file=paste(path.result,"/BVAR_2008",sep=""))
  }
}
